### 2021-06-13 docs/manuscript/manuscript.tex
Refer to S2_Fig in methods
In response to Reviewer #1, Minor Points, 2, g.
Improve discussion about I4-FFL and constitutive expression

The phenotype of a GRN was defined as the expression pattern of each gene along
the morphogenetic field after 500 time steps of integration of the dynamical
system. We chose that number of time steps because numerical experiments showed
that GRNs reached the steady state in approximately 300 steps.

@@

However, as our model was less stringent, we found a larger number of possible
topologies with the same striped phenotype.\\

@@

We also found topologies with a similar topology to that of the “opposing
gradients” reported by Schaerli et al.~\cite{Schaerli2018,Schaerli2014}.
Although the “opposing gradients” mechanism requires the constitutive expression
of two of the genes in the GRN, and our model does not take constitutive
expression into account, we realized that the GRNs that presented the “opposing
gradients” topology, had also commonly positive auto-regulation interactions on
these two nodes, supplying in this way the lack of constitutive expression.

>>>>

The phenotype of a GRN was defined as the expression pattern of each gene along
the morphogenetic field after 500 time steps of integration of the dynamical
system. We chose that number of time steps because numerical experiments showed
that GRNs reached the steady state in approximately 300 steps (\nameref{S2_Fig}).

@@

However, as our model was less stringent and allowed the morphogen input to
interact with any gene, we found a larger number of possible topologies with the
same striped phenotype. For example, in a single input model the I4-FFL could
not produce a stripe of gene expression~\cite{munteanu_2014}, whereas in our
experimental setup 20.17\% of the topologies presented this motif as a
subgraph~(\nameref{S1_Table}).

@@

We also found topologies with a similar topology to that of the “opposing
gradients” reported by Schaerli et al.~\cite{Schaerli2018,Schaerli2014}.
Although the “opposing gradients” mechanism requires the constitutive expression
of two of the genes in the GRN, and our model does not take constitutive
expression into account, we realized that the GRNs that presented the “opposing
gradients” topology, had also commonly positive auto-regulation interactions on
these two nodes, supplying in this way the lack of constitutive
expression as found in previous studies~\cite{munteanu_2014}.
